---
title: "housing"
author: "Blandon Lee"
date: "2/7/2022"
output: html_document
---

What I cleaned from the data set is the variables. They were in differing formats that made it difficult to use.

```{r}
library(readxl)
housing <- read_excel("C:/Users/bland/Desktop/DSC 520/Data/housing.xlsx")
View(housing)
```
```{r}
names(housing) <- make.names(names(housing))
```
```{r}
summary(housing)
```

I chose to use the predictors LivingSgft, Bedrooms, and FullBaths because I felt that this information is desired by most people buying homes.They are also important for sales because it is a measuring stick for a home's value on the market.  Everyone needs these answers prior to a purchase or sale to ensure the home works for the buyer and is priced accordingly.

```{r}
price_lot <- data.frame(housing$SalePrice, housing$LotSqft)
price_lot

# Created Variable

summary(price_lot)
```
```{r}
price_sqft_bed_bath <- data.frame(housing$SalePrice, housing$LivingSqft, housing$Bedrooms, housing$FullBaths)
price_sqft_bed_bath

# Created Variable

summary(price_sqft_bed_bath)
```

When I ran the summary function on SalePrice/LotSqft I got a multiple R-squared: 0.01435 and adjusted R-squared:  0.01428. When I ran the summary function on  SalePrice/LivingSqft/FullBaths/Bedrooms I got a multiple R-squared:  0.212,	adjusted R-squared:  0.2118. 

With a decrease in adjusted R-squared is shows that it does not improve the model fit. With additions to the dataset the effect seems to be the same.

```{r}
RegModel.2 <- lm(housing.SalePrice~housing.LotSqft, data=price_lot)

# R-squared / Adjusted R-squared

summary(RegModel.2)
```
```{r}
LinearModel.3 <- lm(housing.SalePrice ~ housing.LivingSqft + 
  housing.FullBaths + housing.Bedrooms, data=price_sqft_bed_bath)

# R-squared / Adjusted R-squared

summary(LinearModel.3)
```

There is a 99% probability that the mean will fall within lower bound and upper bound intervals. With the mean falling between the lower and upper bounds in all the examples I am confident that 99% of the samples contain true parameters.

```{r}
with(price_lot, (t.test(housing.SalePrice, housing.LotSqft, 
  alternative='two.sided', conf.level=.99, paired=TRUE)))

# Calculate the confidence intervals 
```
```{r}
with(price_sqft_bed_bath, (t.test(housing.SalePrice, housing.Bedrooms, 
  alternative='two.sided', conf.level=.99, paired=TRUE)))

with(price_sqft_bed_bath, (t.test(housing.SalePrice, housing.FullBaths, 
  alternative='two.sided', conf.level=.99, paired=TRUE)))

with(price_sqft_bed_bath, (t.test(housing.SalePrice, housing.LivingSqft, 
  alternative='two.sided', conf.level=.99, paired=TRUE)))

# Calculate the confidence intervals
```



```{r}
original <- aov(SalePrice ~ LivingSqft + Bedrooms + FullBaths, data = housing)
summary(original)
```
```{r}
one.way <- aov(housing$SalePrice ~ housing$LotSqft , data = price_lot)
summary(one.way)

two.way <- aov(housing$SalePrice ~ housing$LivingSqft + housing$Bedrooms + housing$FullBaths, data = price_sqft_bed_bath)
summary(two.way)

# Analysis of variance
```


```{r} 
PriceLot <- lm(housing.SalePrice ~ housing.LotSqft, data = price_lot)
PriceLot

library(car)
outlierTest(PriceLot)
# Accessing Outliers
```
```{r}
qqPlot(PriceLot, main="QQ Plot")
leveragePlots(PriceLot)
```
```{r}
PriceBLF <- (lm(housing.SalePrice ~ housing.Bedrooms + housing.LivingSqft + housing.FullBaths, data = price_sqft_bed_bath))
PriceBLF

library(car)
outlierTest(PriceBLF)
# Accessing Outliers
```
```{r}
qqPlot(PriceBLF, main="QQ Plot")
leveragePlots(PriceBLF)
```


```{r}
summary(PriceLot)
StandardRes <- rstandard(PriceLot)

plot(StandardRes)
hist(StandardRes)
# standardized residuals
```

```{r}
summary(PriceBLF)
Standard_Res <- rstandard(PriceBLF)

plot(Standard_Res)
hist(Standard_Res)
# standardized residuals
```

```{r}
summary(PriceBLF$residuals)
summary(PriceLot$residuals)
# Pull out residuals
```

```{r}
summary(PriceBLF)
summary(PriceLot)

leverage_1 <- as.data.frame(hatvalues(PriceBLF))
leverage_1
plot(hatvalues(PriceBLF), type = 'h')


leverage_2 <- as.data.frame(hatvalues(PriceLot))
leverage_2
plot(hatvalues(PriceLot), type = 'h')

# Calculate leverage
```

```{r}
cooks_d <- cooks.distance(PriceBLF)
cooks_d

n <- nrow(outlierTest(PriceBLF))
plot(cooks_d, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")

# Cooks Distance

```
```{r}
cooks_d2 <- cooks.distance(PriceLot)
cooks_d2

n <- nrow(outlierTest(PriceLot)) 
plot(cooks_d2, main = "Cooks Distance for Influential Obs")
abline(h = 4/n, lty = 2, col = "steelblue")

# Cooks Distance
```

```{r}
cov(price_lot)
cov(price_sqft_bed_bath)

# Covariance
```










